---
title: "MATH 216 Homework 5"
author: "Jacob Dixon"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(stringr)
library(tm)
library(wordcloud)
library(SnowballC)
library(tidyr)
library(shiny)
library(ggplot2)
library(ggthemes)
```

## Admistrative:

Please indicate

* Who you collaborated with:Alison Cook
* Roughly how much time you spent on this HW:3h
* What gave you the most trouble: Uploading shiny w/windows
* Any comments you have: What is the domain for the Middlebury shiny server? I.E. MIDD\jdixon



## Question 1:

* Pick three books from [Project Gutenberg](https://www.gutenberg.org/) and make
a "single-file" Shiny app based on file `App.R`
    + showing the corresponding wordcloud for a given book
    + that has "toggle" functionality to switch between the three books
* Note: Project Gutenberg tends to have older books whose copyright has expired.
* Install all necessary packages on your Middlebury Shiny server account
following the instructions given in Lec16 Shiny.
* Upload your app to the Middlebury Shiny server and replace the NHL link with
the link for your app [here](http://shiny.middlebury.edu/jdixon/wordcloud/), so that when you Knit the 
document a working hyperlink shows.

Hints:

* Get your code completely working for a non-Shiny app first, then build your
app slowly.
* If you get stuck, please ask for help sooner rather than later. I don't want 
people spinning their wheels on this HW this late in the semester.
* Consider using `if` and `else` statements to switch out which text to show the
wordcloud for. Note this isn't the only way to do this. Ex:

```{r, cache=TRUE, echo=FALSE}

#Import the three books
proposal <-
  readLines("a_modest_proposal.txt", encoding="UTF-8") %>%
  as.character()

moby_dick <-
  readLines("moby_dick.txt", encoding="UTF-8") %>%
  as.character()

tom_sawyer <-
  readLines("tom_sawyer.txt", encoding="UTF-8") %>%
  as.character()


#Clean up the text for each:
# For Modest Proposal
proposal <- proposal %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()


#For Moby Dick
moby_dick <- moby_dick %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()

#For Tom Sawyer
tom_sawyer <- tom_sawyer %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()



#Create the word clouds
#Modest Proposal
proposal <- VectorSource(proposal) %>% 
  Corpus()
wordcloud(proposal, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))

#Moby Dick
moby_dick <- VectorSource(moby_dick) %>% 
  Corpus()
wordcloud(moby_dick, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))


#Tom Sawyer
tom_sawyer <- VectorSource(tom_sawyer) %>% 
  Corpus()
wordcloud(tom_sawyer, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))


```

